DataGatheringandAnalysis

### 2014-11-11 GEMDataSource.Rmd
Small edits - need to get rid of hyphens in data

```{r}
# Set working directory
setwd('~/Assign2Education/')

@@

# Rename columns
CFearFail <- plyr::rename(x = CFearFail, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Fear"))

@@

# Rename columns
CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Owner"))

@@

# Rename columns
CEntreIntention <- plyr::rename(x = CEntreIntention, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Intention"))

@@

# Rename columns
CNascentEntre <- plyr::rename(x = CNascentEntre, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Nascent"))

@@

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Perceived"))

# Merge the data
MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

@@

>>>>

```{r echo =FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

@@

# Rename columns
CFearFail <- plyr::rename(x = CFearFail, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentFear"))

@@

# Rename columns
CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOwner"))

@@

# Rename columns
CEntreIntention <- plyr::rename(x = CEntreIntention, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentIntention"))

@@

# Rename columns
CNascentEntre <- plyr::rename(x = CNascentEntre, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentNascent"))

@@

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentPerceived"))

#### Merge the data ####
MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

@@

# Convert year columns to numeric
FinalMerge[,2001:2012] <- as.numeric(FinalMerge[,2001:2012])

# Need to figure out how to get rid of "-" in data

summary(FinalMerge)
# Run a regression
R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
R1
